Is malaria control profitable? Return on investment of privately-managed residential fumigations at a large sugarcane processing facility in Southern Mozambique

### 2018-04-28 inst/rmd/paper.tex
big update

\(\hat{Y}_{it}\) is the rate of absence. \(\beta_{1}\) is the binary
``season'' variable, imputed from overall district clinical incidence.
Our intervention is whether the residence of the worker in question was
treated in the last year, and, if so, the time since treatment,
represented, respectively, by \(\beta_{2}\) and \(\beta_{3}\).
\(\alpha_i\) reprsents the time invariant worker fixed effects, and
\(\delta_i\) represents the fixed effect of the particular malaria
season. \(\upsilon\) is the error term.

@@

\begin{table}[ht]
\centering
\begin{tabular}{rlllll}
  \hline
Variable &   & Treatment workers & Treatment days & Control workers & Control days \\ 
  \hline
Department & Administrative &  35 & 12523 & 157 & 173151 \\ 
   & Factory &  71 & 20533 & 453 & 280416 \\ 
   & Field & 410 & 91302 & 2691 & 1181175 \\ 
  Sex & F & 228 & 47907 & 1274 & 489484 \\ 
   & M & 288 & 76451 & 2027 & 1145258 \\ 
  Status & Permanent & 127 & 47075 & 500 & 655311 \\ 
   & Temporary & 389 & 77283 & 2801 & 979431 \\ 
  Age & 20 & 140 & 29463 & 960 & 347758 \\ 
   & 30 & 176 & 39119 & 1225 & 550783 \\ 
   & 40 & 123 & 30186 & 652 & 366936 \\ 
   & 50 &  58 & 18881 & 344 & 268877 \\ 
   & 60 &  17 & 5893 & 116 & 96555 \\ 
   & 70 &   2 & 816 &   4 & 3833 \\ 
   \hline
\end{tabular}
\caption{Overall worker characteristics} 
\end{table}

@@

{\centering \includegraphics{figures/unnamed-chunk-19-1}

\caption{Age distribution by sex and worker status}\label{fig:unnamed-chunk-19}
\end{figure}

@@

\caption{i. Monthly total precipitation in the Maniça district; ii. Average monthly temperature (bars) during the study period, as well as monthly maximum (red) and minimum (blue) temperatures}\label{fig:unnamed-chunk-20}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{figures/unnamed-chunk-21-1.pdf}
\caption{Clinical malaria (district of Manhiça), all-cause absenteeism
among Maragra workers, sick absenteeism among Maragra workers, positive
cases at company clinic, and test positivity rate at company clinic}
\end{figure}

\textbf{Fumigations}: During the period from January 1st, 2013 through
December 31st, 2016, the Maragra Malaria Control Unit carried out 11,007
episodes of fumigation of residential ``agregados'' (household
combinations), for a total of 13,260 building-fumigation combinations.
The total number of unique agregados sprayed during this period was
3,998. Among the 3,362 workers for whom we have reliable absenteeism and
residential data, 692 had their homes fumigated at least once (the
majority of workers live off of the facility).

@@

{\centering \includegraphics{figures/unnamed-chunk-26-1}

@@

\caption{Rainfall and absenteeism: association of any rainfall with absenteeism rate (left) and association of rainfall amount and absenteeism (right)}\label{fig:unnamed-chunk-26}
\end{figure}

@@

\begin{table}

\caption{\label{tab:unnamed-chunk-28}All cause absenteeism: model results}
\centering
\begin{tabular}[t]{ll}
\toprule
Term & Estimate\\
\midrule
\addlinespace[1.5em]
\multicolumn{2}{l}{\textbf{Permanent field worker}}\\
\hspace{1em}Malaria season & 2.533 (P<0.001)\\
\hspace{1em}Months since IRS: 01 & 5.382 (P<0.001)\\
\hspace{1em}Months since IRS: 02-04 & 4.747 (P<0.001)\\
\hspace{1em}Months since IRS: 05-09 & -2.669 (P<0.001)\\
\hspace{1em}Precipitation (mm) & 0.206 (P<0.001)\\
\hspace{1em}Malaria season:Months since IRS: 01 & -6.262 (P<0.001)\\
\hspace{1em}Malaria season:Months since IRS: 02-04 & -8.388 (P<0.001)\\
\hspace{1em}Malaria season:Months since IRS: 05-09 & -3.71 (P<0.001)\\
\addlinespace[1.5em]
\multicolumn{2}{l}{\textbf{Permanent not field worker}}\\
\hspace{1em}Malaria season & 0.957 (P<0.001)\\
\hspace{1em}Months since IRS: 01 & -0.987 (P=0.071)\\
\hspace{1em}Months since IRS: 02-04 & 4.375 (P<0.001)\\
\hspace{1em}Months since IRS: 05-09 & -0.55 (P=0.254)\\
\hspace{1em}Precipitation (mm) & 0.548 (P<0.001)\\
\hspace{1em}Malaria season:Months since IRS: 01 & 1.787 (P=0.016)\\
\hspace{1em}Malaria season:Months since IRS: 02-04 & -5.208 (P<0.001)\\
\hspace{1em}Malaria season:Months since IRS: 05-09 & -2.04 (P=0.003)\\
\addlinespace[1.5em]
\multicolumn{2}{l}{\textbf{Temporary field worker}}\\
\hspace{1em}Malaria season & -0.368 (P<0.001)\\
\hspace{1em}Months since IRS: 01 & -0.075 (P=0.526)\\
\hspace{1em}Months since IRS: 02-04 & -0.193 (P=0.072)\\
\hspace{1em}Months since IRS: 05-09 & -0.036 (P=0.738)\\
\hspace{1em}Precipitation (mm) & 0.02 (P<0.001)\\
\hspace{1em}Malaria season:Months since IRS: 01 & -0.154 (P=0.406)\\
\hspace{1em}Malaria season:Months since IRS: 02-04 & 0.297 (P=0.05)\\
\hspace{1em}Malaria season:Months since IRS: 05-09 & 0.041 (P=0.769)\\
\addlinespace[1.5em]
\multicolumn{2}{l}{\textbf{Temporary not field worker}}\\
\hspace{1em}Malaria season & 2.025 (P<0.001)\\
\hspace{1em}Months since IRS: 01 & -2.536 (P=0.134)\\
\hspace{1em}Months since IRS: 02-04 & -1.177 (P=0.282)\\
\hspace{1em}Months since IRS: 05-09 & -1.821 (P=0.084)\\
\hspace{1em}Precipitation (mm) & 0.078 (P<0.001)\\
\hspace{1em}Malaria season:Months since IRS: 01 & 6.121 (P=0.002)\\
\hspace{1em}Malaria season:Months since IRS: 02-04 & 1.333 (P=0.343)\\
\hspace{1em}Malaria season:Months since IRS: 05-09 & -4.639 (P<0.001)\\
\bottomrule
\end{tabular}
\end{table}

@@

\begin{table}

\caption{\label{tab:unnamed-chunk-29}Sick absenteeism only: model results}
\centering
\begin{tabular}[t]{ll}
\toprule
Term & Estimate\\
\midrule
\addlinespace[1.5em]
\multicolumn{2}{l}{\textbf{Permanent field worker}}\\
\hspace{1em}Malaria season & -0.073 (P=0.089)\\
\hspace{1em}Months since IRS: 01 & 0.891 (P<0.001)\\
\hspace{1em}Months since IRS: 02-04 & 1.223 (P<0.001)\\
\hspace{1em}Months since IRS: 05-09 & -0.236 (P=0.249)\\
\hspace{1em}Precipitation (mm) & 0 (P=0.984)\\
\hspace{1em}Malaria season:Months since IRS: 01 & -1.501 (P<0.001)\\
\hspace{1em}Malaria season:Months since IRS: 02-04 & -0.597 (P=0.031)\\
\hspace{1em}Malaria season:Months since IRS: 05-09 & -0.484 (P=0.097)\\
\addlinespace[1.5em]
\multicolumn{2}{l}{\textbf{Permanent not field worker}}\\
\hspace{1em}Malaria season & -0.056 (P=0.204)\\
\hspace{1em}Months since IRS: 01 & -0.667 (P=0.003)\\
\hspace{1em}Months since IRS: 02-04 & 0.904 (P<0.001)\\
\hspace{1em}Months since IRS: 05-09 & 0.127 (P=0.526)\\
\hspace{1em}Precipitation (mm) & -0.002 (P=0.565)\\
\hspace{1em}Malaria season:Months since IRS: 01 & 1.121 (P<0.001)\\
\hspace{1em}Malaria season:Months since IRS: 02-04 & -0.122 (P=0.652)\\
\hspace{1em}Malaria season:Months since IRS: 05-09 & 1.198 (P<0.001)\\
\addlinespace[1.5em]
\multicolumn{2}{l}{\textbf{Temporary field worker}}\\
\hspace{1em}Malaria season & -0.106 (P<0.001)\\
\hspace{1em}Months since IRS: 01 & 0.029 (P=0.545)\\
\hspace{1em}Months since IRS: 02-04 & 0.04 (P=0.35)\\
\hspace{1em}Months since IRS: 05-09 & -0.046 (P=0.291)\\
\hspace{1em}Precipitation (mm) & 0 (P=0.966)\\
\hspace{1em}Malaria season:Months since IRS: 01 & -0.108 (P=0.148)\\
\hspace{1em}Malaria season:Months since IRS: 02-04 & -0.032 (P=0.595)\\
\hspace{1em}Malaria season:Months since IRS: 05-09 & -0.052 (P=0.36)\\
\addlinespace[1.5em]
\multicolumn{2}{l}{\textbf{Temporary not field worker}}\\
\hspace{1em}Malaria season & -0.135 (P=0.236)\\
\hspace{1em}Months since IRS: 01 & 1.427 (P=0.092)\\
\hspace{1em}Months since IRS: 02-04 & -0.569 (P=0.299)\\
\hspace{1em}Months since IRS: 05-09 & -1.42 (P=0.007)\\
\hspace{1em}Precipitation (mm) & -0.005 (P=0.613)\\
\hspace{1em}Malaria season:Months since IRS: 01 & -1.796 (P=0.069)\\
\hspace{1em}Malaria season:Months since IRS: 02-04 & 2.479 (P<0.001)\\
\hspace{1em}Malaria season:Months since IRS: 05-09 & 0.18 (P=0.794)\\
\bottomrule
\end{tabular}
\end{table}

@@

\begin{figure}
\centering
\includegraphics{figures/unnamed-chunk-33-1.pdf}
\caption{i. Absenteeism before and after IRS administration for all
workers who ever received IRS; ii. The same, but segregated by malaria
and non-malaria seasons}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{figures/unnamed-chunk-34-1.pdf}
\caption{i. Sick absenteeism before and after IRS administration for all
workers who ever received IRS; ii. The same, but segregated by malaria
and non-malaria seasons}
\end{figure}

>>>>

\(\hat{Y}_{it}\) is the rate of absence. \(\beta_{1}\) is the binary
``season'' variable, imputed from overall district clinical incidence.
Our intervention is whether the residence of the worker in question was
treated in the last year, and, if so, the time since treatment,
represented, respectively, by \(\beta_{2}\) and \(\beta_{3}\).
\(\alpha_i\) represents the time invariant worker fixed effects, and
\(\delta_i\) represents the fixed effect of the particular malaria
season. \(\upsilon\) is the error term.

@@

\begin{table}[ht]
\centering
\begin{tabular}{rlllll}
  \hline
Variable &   & Treatment workers & Treatment days & Control workers & Control days \\ 
  \hline
Department & Administrative & 157 & 185674 &   0 &   0 \\ 
   & Factory & 459 & 300949 &   0 &   0 \\ 
   & Field & 2746 & 1272477 &   0 &   0 \\ 
  Sex & F & 1305 & 537391 &   0 &   0 \\ 
   & M & 2057 & 1221709 &   0 &   0 \\ 
  Status & Permanent & 500 & 702386 &   0 &   0 \\ 
   & Temporary & 2862 & 1056714 &   0 &   0 \\ 
  Age & 20 & 985 & 377221 &   0 &   0 \\ 
   & 30 & 1244 & 589902 &   0 &   0 \\ 
   & 40 & 665 & 397122 &   0 &   0 \\ 
   & 50 & 347 & 287758 &   0 &   0 \\ 
   & 60 & 117 & 102448 &   0 &   0 \\ 
   & 70 &   4 & 4649 &   0 &   0 \\ 
   \hline
\end{tabular}
\caption{Overall worker characteristics} 
\end{table}

@@

@@

\caption{Age distribution by sex and worker status}\label{fig:unnamed-chunk-20}
\end{figure}

{\centering \includegraphics{figures/unnamed-chunk-21-1}

\caption{i. Monthly total precipitation in the Maniça district; ii. Average monthly temperature (bars) during the study period, as well as monthly maximum (red) and minimum (blue) temperatures}\label{fig:unnamed-chunk-21}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{figures/unnamed-chunk-22-1.pdf}
\caption{Clinical malaria (district of Manhiça), all-cause absenteeism
among Maragra workers, sick absenteeism among Maragra workers, positive
cases at company clinic, and test positivity rate at company clinic}
\end{figure}

\textbf{Fumigations}: During the period from January 1st, 2013 through
December 31st, 2016, the Maragra Malaria Control Unit carried out 11,007
episodes of fumigation of residential ``agregados'' (household
combinations), for a total of 13,260 building-fumigation combinations.
The total number of unique agregados sprayed during this period was
3,998. Among the 3,362 workers for whom we have reliable absenteeism and
residential data, 562 had their homes fumigated at least once (the
majority of workers live off of the facility).

@@

{\centering \includegraphics{figures/unnamed-chunk-27-1}

@@

\caption{Rainfall and absenteeism: association of any rainfall with absenteeism rate (left) and association of rainfall amount and absenteeism (right)}\label{fig:unnamed-chunk-27}
\end{figure}

@@

\begin{longtable}[t]{ll}
\caption{\label{tab:unnamed-chunk-28}All cause absenteeism: model results}\\
\toprule
Term & Estimate\\
\midrule
\endfirsthead
\caption[]{All cause absenteeism: model results \textit{(continued)}}\\
\toprule
Term & Estimate\\
\midrule
\endhead
\
\endfoot
\bottomrule
\endlastfoot
\addlinespace[1.5em]
\multicolumn{2}{l}{\textbf{Permanent field worker}}\\
\hspace{1em}Malaria season & 2.458 (P<0.001)\\
\hspace{1em}Months since IRS: 00 & 4.838 (P<0.001)\\
\hspace{1em}Months since IRS: 01 & 6.013 (P<0.001)\\
\hspace{1em}Months since IRS: 02 & 5.395 (P<0.001)\\
\hspace{1em}Months since IRS: 03 & 5.596 (P<0.001)\\
\hspace{1em}Months since IRS: 04 & 2.47 (P=0.052)\\
\hspace{1em}Months since IRS: 05 & 2.925 (P=0.015)\\
\hspace{1em}Rainy day & 2.236 (P<0.001)\\
\hspace{1em}Malaria season:Months since IRS: 00 & -10.488 (P<0.001)\\
\hspace{1em}Malaria season:Months since IRS: 01 & -1.828 (P=0.187)\\
\hspace{1em}Malaria season:Months since IRS: 02 & -7.825 (P<0.001)\\
\hspace{1em}Malaria season:Months since IRS: 03 & -10.95 (P<0.001)\\
\hspace{1em}Malaria season:Months since IRS: 04 & -5.517 (P<0.001)\\
\hspace{1em}Malaria season:Months since IRS: 05 & -11.014 (P<0.001)\\
\addlinespace[1.5em]
\multicolumn{2}{l}{\textbf{Permanent not field worker}}\\
\hspace{1em}Malaria season & 0.955 (P<0.001)\\
\hspace{1em}Months since IRS: 00 & -2.358 (P=0.002)\\
\hspace{1em}Months since IRS: 01 & 0.709 (P=0.356)\\
\hspace{1em}Months since IRS: 02 & 2.866 (P<0.001)\\
\hspace{1em}Months since IRS: 03 & 6.045 (P<0.001)\\
\hspace{1em}Months since IRS: 04 & 4.113 (P<0.001)\\
\hspace{1em}Months since IRS: 05 & -0.144 (P=0.877)\\
\hspace{1em}Rainy day & 4.503 (P<0.001)\\
\hspace{1em}Malaria season:Months since IRS: 00 & 2.792 (P=0.008)\\
\hspace{1em}Malaria season:Months since IRS: 01 & 0.502 (P=0.625)\\
\hspace{1em}Malaria season:Months since IRS: 02 & -5.816 (P<0.001)\\
\hspace{1em}Malaria season:Months since IRS: 03 & -4.871 (P<0.001)\\
\hspace{1em}Malaria season:Months since IRS: 04 & -5.815 (P<0.001)\\
\hspace{1em}Malaria season:Months since IRS: 05 & 1.719 (P=0.183)\\
\addlinespace[1.5em]
\multicolumn{2}{l}{\textbf{Temporary field worker}}\\
\hspace{1em}Malaria season & -0.356 (P<0.001)\\
\hspace{1em}Months since IRS: 00 & -0.093 (P=0.57)\\
\hspace{1em}Months since IRS: 01 & -0.006 (P=0.972)\\
\hspace{1em}Months since IRS: 02 & -0.232 (P=0.156)\\
\hspace{1em}Months since IRS: 03 & -0.177 (P=0.305)\\
\hspace{1em}Months since IRS: 04 & -0.059 (P=0.763)\\
\hspace{1em}Months since IRS: 05 & 0.039 (P=0.86)\\
\hspace{1em}Rainy day & 0.028 (P=0.236)\\
\hspace{1em}Malaria season:Months since IRS: 00 & -0.114 (P=0.659)\\
\hspace{1em}Malaria season:Months since IRS: 01 & -0.269 (P=0.301)\\
\hspace{1em}Malaria season:Months since IRS: 02 & -0.212 (P=0.432)\\
\hspace{1em}Malaria season:Months since IRS: 03 & 0.127 (P=0.628)\\
\hspace{1em}Malaria season:Months since IRS: 04 & 0.808 (P=0.002)\\
\hspace{1em}Malaria season:Months since IRS: 05 & 0.682 (P=0.013)\\
\addlinespace[1.5em]
\multicolumn{2}{l}{\textbf{Temporary not field worker}}\\
\hspace{1em}Malaria season & 1.897 (P<0.001)\\
\hspace{1em}Months since IRS: 00 & -0.929 (P=0.726)\\
\hspace{1em}Months since IRS: 01 & -2.264 (P=0.251)\\
\hspace{1em}Months since IRS: 02 & 1.086 (P=0.517)\\
\hspace{1em}Months since IRS: 03 & 2.083 (P=0.218)\\
\hspace{1em}Months since IRS: 04 & -4.187 (P=0.02)\\
\hspace{1em}Months since IRS: 05 & -3.224 (P=0.111)\\
\hspace{1em}Rainy day & 1.053 (P<0.001)\\
\hspace{1em}Malaria season:Months since IRS: 00 & 0.754 (P=0.797)\\
\hspace{1em}Malaria season:Months since IRS: 01 & 14.058 (P<0.001)\\
\hspace{1em}Malaria season:Months since IRS: 02 & -3.674 (P=0.128)\\
\hspace{1em}Malaria season:Months since IRS: 03 & -3.644 (P=0.119)\\
\hspace{1em}Malaria season:Months since IRS: 04 & 12.4 (P<0.001)\\
\hspace{1em}Malaria season:Months since IRS: 05 & -2.697 (P=0.334)\\*
\end{longtable}

@@

\begin{longtable}[t]{ll}
\caption{\label{tab:unnamed-chunk-29}Sick absenteeism only: model results}\\
\toprule
Term & Estimate\\
\midrule
\endfirsthead
\caption[]{Sick absenteeism only: model results \textit{(continued)}}\\
\toprule
Term & Estimate\\
\midrule
\endhead
\
\endfoot
\bottomrule
\endlastfoot
\addlinespace[1.5em]
\multicolumn{2}{l}{\textbf{Permanent field worker}}\\
\hspace{1em}Malaria season & -0.068 (P=0.116)\\
\hspace{1em}Months since IRS: 00 & 1.358 (P<0.001)\\
\hspace{1em}Months since IRS: 01 & 0.511 (P=0.141)\\
\hspace{1em}Months since IRS: 02 & 2.272 (P<0.001)\\
\hspace{1em}Months since IRS: 03 & 1.21 (P<0.001)\\
\hspace{1em}Months since IRS: 04 & -0.057 (P=0.889)\\
\hspace{1em}Months since IRS: 05 & -0.295 (P=0.442)\\
\hspace{1em}Rainy day & -0.053 (P=0.207)\\
\hspace{1em}Malaria season:Months since IRS: 00 & -2.046 (P<0.001)\\
\hspace{1em}Malaria season:Months since IRS: 01 & -1.037 (P=0.019)\\
\hspace{1em}Malaria season:Months since IRS: 02 & -1.691 (P<0.001)\\
\hspace{1em}Malaria season:Months since IRS: 03 & -0.428 (P=0.365)\\
\hspace{1em}Malaria season:Months since IRS: 04 & 0.52 (P=0.305)\\
\hspace{1em}Malaria season:Months since IRS: 05 & -0.617 (P=0.257)\\
\addlinespace[1.5em]
\multicolumn{2}{l}{\textbf{Permanent not field worker}}\\
\hspace{1em}Malaria season & -0.056 (P=0.216)\\
\hspace{1em}Months since IRS: 00 & -0.315 (P=0.317)\\
\hspace{1em}Months since IRS: 01 & -1.009 (P=0.002)\\
\hspace{1em}Months since IRS: 02 & -0.504 (P=0.131)\\
\hspace{1em}Months since IRS: 03 & 1.483 (P<0.001)\\
\hspace{1em}Months since IRS: 04 & 2.029 (P<0.001)\\
\hspace{1em}Months since IRS: 05 & -0.266 (P=0.492)\\
\hspace{1em}Rainy day & -0.012 (P=0.785)\\
\hspace{1em}Malaria season:Months since IRS: 00 & 0.65 (P=0.137)\\
\hspace{1em}Malaria season:Months since IRS: 01 & 1.491 (P<0.001)\\
\hspace{1em}Malaria season:Months since IRS: 02 & 1.06 (P=0.016)\\
\hspace{1em}Malaria season:Months since IRS: 03 & -0.973 (P=0.035)\\
\hspace{1em}Malaria season:Months since IRS: 04 & -0.709 (P=0.158)\\
\hspace{1em}Malaria season:Months since IRS: 05 & 2.82 (P<0.001)\\
\addlinespace[1.5em]
\multicolumn{2}{l}{\textbf{Temporary field worker}}\\
\hspace{1em}Malaria season & -0.104 (P<0.001)\\
\hspace{1em}Months since IRS: 00 & 0.204 (P=0.002)\\
\hspace{1em}Months since IRS: 01 & -0.137 (P=0.03)\\
\hspace{1em}Months since IRS: 02 & -0.056 (P=0.392)\\
\hspace{1em}Months since IRS: 03 & 0.122 (P=0.077)\\
\hspace{1em}Months since IRS: 04 & 0.061 (P=0.432)\\
\hspace{1em}Months since IRS: 05 & -0.163 (P=0.063)\\
\hspace{1em}Rainy day & -0.018 (P=0.05)\\
\hspace{1em}Malaria season:Months since IRS: 00 & -0.307 (P=0.003)\\
\hspace{1em}Malaria season:Months since IRS: 01 & 0.107 (P=0.306)\\
\hspace{1em}Malaria season:Months since IRS: 02 & 0.064 (P=0.557)\\
\hspace{1em}Malaria season:Months since IRS: 03 & 0.077 (P=0.464)\\
\hspace{1em}Malaria season:Months since IRS: 04 & -0.185 (P=0.079)\\
\hspace{1em}Malaria season:Months since IRS: 05 & 0.056 (P=0.613)\\
\addlinespace[1.5em]
\multicolumn{2}{l}{\textbf{Temporary not field worker}}\\
\hspace{1em}Malaria season & -0.15 (P=0.191)\\
\hspace{1em}Months since IRS: 00 & -0.401 (P=0.765)\\
\hspace{1em}Months since IRS: 01 & 2.063 (P=0.038)\\
\hspace{1em}Months since IRS: 02 & -0.508 (P=0.549)\\
\hspace{1em}Months since IRS: 03 & 0.019 (P=0.982)\\
\hspace{1em}Months since IRS: 04 & -1.905 (P=0.036)\\
\hspace{1em}Months since IRS: 05 & -2.031 (P=0.047)\\
\hspace{1em}Rainy day & -0.036 (P=0.711)\\
\hspace{1em}Malaria season:Months since IRS: 00 & 0.005 (P=0.997)\\
\hspace{1em}Malaria season:Months since IRS: 01 & -2.43 (P=0.071)\\
\hspace{1em}Malaria season:Months since IRS: 02 & 0.083 (P=0.946)\\
\hspace{1em}Malaria season:Months since IRS: 03 & -1.915 (P=0.105)\\
\hspace{1em}Malaria season:Months since IRS: 04 & 5.662 (P<0.001)\\
\hspace{1em}Malaria season:Months since IRS: 05 & 1.729 (P=0.22)\\*
\end{longtable}

\subsection{Externalities}\label{externalities-1}

Below are model results for the full protection model.

\begin{longtable}[t]{ll}
\caption{\label{tab:unnamed-chunk-30}All absenteeism with herd immunity: model results}\\
\toprule
Term & Estimate\\
\midrule
\endfirsthead
\caption[]{All absenteeism with herd immunity: model results \textit{(continued)}}\\
\toprule
Term & Estimate\\
\midrule
\endhead
\
\endfoot
\bottomrule
\endlastfoot
\addlinespace[1.5em]
\multicolumn{2}{l}{\textbf{Permanent field worker}}\\
\hspace{1em}Malaria season & 3.595 (P<0.001)\\
\hspace{1em}Months since IRS: 00 & 4.684 (P<0.001)\\
\hspace{1em}Months since IRS: 01 & 7.368 (P<0.001)\\
\hspace{1em}Months since IRS: 02 & 7.572 (P<0.001)\\
\hspace{1em}Months since IRS: 03 & 7.675 (P<0.001)\\
\hspace{1em}Months since IRS: 04 & 3.808 (P=0.005)\\
\hspace{1em}Months since IRS: 05 & 3.612 (P=0.004)\\
\hspace{1em}Rainy day & 3.251 (P<0.001)\\
\hspace{1em}Herd protection & -0.208 (P<0.001)\\
\hspace{1em}Malaria season:Months since IRS: 00 & -10.583 (P<0.001)\\
\hspace{1em}Malaria season:Months since IRS: 01 & -2.757 (P=0.061)\\
\hspace{1em}Malaria season:Months since IRS: 02 & -8.816 (P<0.001)\\
\hspace{1em}Malaria season:Months since IRS: 03 & -11.784 (P<0.001)\\
\hspace{1em}Malaria season:Months since IRS: 04 & -6.39 (P<0.001)\\
\hspace{1em}Malaria season:Months since IRS: 05 & -12.58 (P<0.001)\\
\addlinespace[1.5em]
\multicolumn{2}{l}{\textbf{Permanent not field worker}}\\
\hspace{1em}Malaria season & 0.812 (P<0.001)\\
\hspace{1em}Months since IRS: 00 & -1.763 (P=0.024)\\
\hspace{1em}Months since IRS: 01 & 1.383 (P=0.083)\\
\hspace{1em}Months since IRS: 02 & 4.06 (P<0.001)\\
\hspace{1em}Months since IRS: 03 & 5.191 (P<0.001)\\
\hspace{1em}Months since IRS: 04 & 4.688 (P<0.001)\\
\hspace{1em}Months since IRS: 05 & -0.158 (P=0.87)\\
\hspace{1em}Rainy day & 4.491 (P<0.001)\\
\hspace{1em}Herd protection & -0.051 (P=0.021)\\
\hspace{1em}Malaria season:Months since IRS: 00 & 2.437 (P=0.025)\\
\hspace{1em}Malaria season:Months since IRS: 01 & 0.144 (P=0.892)\\
\hspace{1em}Malaria season:Months since IRS: 02 & -6.423 (P<0.001)\\
\hspace{1em}Malaria season:Months since IRS: 03 & -2.935 (P=0.011)\\
\hspace{1em}Malaria season:Months since IRS: 04 & -5.391 (P<0.001)\\
\hspace{1em}Malaria season:Months since IRS: 05 & 0.971 (P=0.473)\\
\addlinespace[1.5em]
\multicolumn{2}{l}{\textbf{Temporary field worker}}\\
\hspace{1em}Malaria season & -0.35 (P<0.001)\\
\hspace{1em}Months since IRS: 00 & -0.148 (P=0.351)\\
\hspace{1em}Months since IRS: 01 & -0.22 (P=0.156)\\
\hspace{1em}Months since IRS: 02 & -0.528 (P=0.001)\\
\hspace{1em}Months since IRS: 03 & -0.431 (P=0.012)\\
\hspace{1em}Months since IRS: 04 & -0.285 (P=0.138)\\
\hspace{1em}Months since IRS: 05 & -0.021 (P=0.921)\\
\hspace{1em}Rainy day & 0.071 (P=0.041)\\
\hspace{1em}Herd protection & 0.024 (P<0.001)\\
\hspace{1em}Malaria season:Months since IRS: 00 & -0.165 (P=0.514)\\
\hspace{1em}Malaria season:Months since IRS: 01 & -0.152 (P=0.55)\\
\hspace{1em}Malaria season:Months since IRS: 02 & -0.039 (P=0.884)\\
\hspace{1em}Malaria season:Months since IRS: 03 & 0.149 (P=0.562)\\
\hspace{1em}Malaria season:Months since IRS: 04 & 0.83 (P=0.001)\\
\hspace{1em}Malaria season:Months since IRS: 05 & 0.643 (P=0.017)\\
\addlinespace[1.5em]
\multicolumn{2}{l}{\textbf{Temporary not field worker}}\\
\hspace{1em}Malaria season & 3.49 (P<0.001)\\
\hspace{1em}Months since IRS: 00 & -0.214 (P=0.938)\\
\hspace{1em}Months since IRS: 01 & -1.84 (P=0.374)\\
\hspace{1em}Months since IRS: 02 & 1.463 (P=0.414)\\
\hspace{1em}Months since IRS: 03 & 2.207 (P=0.217)\\
\hspace{1em}Months since IRS: 04 & -4.231 (P=0.024)\\
\hspace{1em}Months since IRS: 05 & -3.542 (P=0.091)\\
\hspace{1em}Rainy day & 0.514 (P=0.101)\\
\hspace{1em}Herd protection & 0.012 (P=0.918)\\
\hspace{1em}Malaria season:Months since IRS: 00 & -0.626 (P=0.837)\\
\hspace{1em}Malaria season:Months since IRS: 01 & 13.506 (P<0.001)\\
\hspace{1em}Malaria season:Months since IRS: 02 & -3.399 (P=0.18)\\
\hspace{1em}Malaria season:Months since IRS: 03 & -3.826 (P=0.115)\\
\hspace{1em}Malaria season:Months since IRS: 04 & 10.956 (P<0.001)\\
\hspace{1em}Malaria season:Months since IRS: 05 & -3.786 (P=0.191)\\*
\end{longtable}

@@

\begin{figure}
\centering
\includegraphics{figures/unnamed-chunk-34-1.pdf}
\caption{i. Absenteeism before and after IRS administration for all
workers who ever received IRS; ii. The same, but segregated by malaria
and non-malaria seasons}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{figures/unnamed-chunk-35-1.pdf}
\caption{i. Sick absenteeism before and after IRS administration for all
workers who ever received IRS; ii. The same, but segregated by malaria
and non-malaria seasons}
\end{figure}
